Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-21 documents/BrazilSlides/slides.tex
Started work on perfect correlations witnessing
Some more progress on the perfect correlation example
Added more the slides, much closer to how we discussed

\usetheme[height=8mm]{Rochester} % Main Theme
\usecolortheme{default} % Color Theme

% \usepackage{pgfpages} % For viewing slides on the right
\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
\AtBeginNote{\scriptsize} % Make notes small
\setbeameroption{show notes} % Shows notes
% \setbeameroption{show only notes} % Shows only notes
% \setbeameroption{show notes on second screen}
\usefonttheme[onlymath]{serif} % For serif font in math mode
\usepackage[backend=biber, style=authoryear, doi=false,isbn=false,url=false, citestyle=authoryear-comp]{biblatex} %

@@

@@

\begin{frame}
    \frametitle{Causal Compatibility}
    \vfill
    \begin{center}
        Triangle Scenario
    \end{center}
    \[ \prob[ABC] = \int_{XYZ}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    \vfill
    \begin{center}
        \noindent\rule{8cm}{0.4pt}
    \end{center}
    \vfill
    \begin{center}
        General Setting
    \end{center}
    \[ \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \qquad \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
    \vfill
\end{frame}

\begin{frame}
    \frametitle{Demonstrating Inflation Technique}
    \vfill
    \begin{center}
    \begin{columns}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_1}}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_1}}
    \end{columns}
    \end{center}
    \only<1>{\[\forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n}\]}%
    \only<2>{\[\AnSub[\graph]{A} \sim \AnSub[\graph']{A_1}\]}%
    \only<3>{\[\AnSub[\graph]{C} \sim \AnSub[\graph']{C_2}\]}%
\end{frame}

@@

\begin{frame}
    \frametitle{Injectable Sets}
    \begin{center}
    \begin{columns}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_2}}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_2}}
    \end{columns}
    \end{center}
    \only<1>{\[\AnSub[\graph]{A,C} \sim \AnSub[\graph']{A_2,C_1}\]}%
    \only<2>{\[?? \not \sim \AnSub[\graph']{B_1,B_2}\]}%
    \only<3>{\[?? \not \sim \AnSub[\graph']{B_2,C_2}\]}%
\end{frame}

\begin{frame}
    \frametitle{Injectable Sets Defined}
    The \term{injectable sets in $\graph'$}:
    \begin{align*}
        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
    The \term{images of the injectable sets in $\graph$}:
    \begin{align*}
        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
\end{frame}

\begin{frame}
    \frametitle{Perfect Correlation Is Incompatible}

\begin{frame}
    \frametitle{Example Inequality}
    \begin{itemize}
        \item Quick example/preview:
    \end{itemize}
    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
    \begin{itemize}
        \item $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
        \item Four outcomes for each $A, B, C$
        \item Polynomial in $\prob[ABC]$, marginals $\prob[AB]$, $\prob[BC]$, $\prob[AC]$, $\prob[A]$, $\prob[B]$, $\prob[C]$
    \end{itemize}
    \note[item]{As a quick example or preview of what is to come, here is a an example inequality admits quantum violations in the triangle scenario}
    \note[item]{Some features of note: inequality is polynomial in $\prob[ABC]$ and its marginals}
\end{frame}

\begin{frame}
    \frametitle{Pre-injectable Sets of Large Inflation}
    \begin{center}
        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{center}
    \begin{itemize}
        \item Has $12$ maximal pre-injectable sets (to follow)
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Deriving Inequalities}
    \begin{itemize}
        \item Inflation facilitates turning linear, inflated inequalities into polynomial deflated ones
        \item \textbf{Question:} How to derive compatibility inequalities for $\graph'$?
        \item \textbf{Answer:} Use your favorite technique for deriving compatibility inequalities:
        \begin{itemize}
            \item Entropic inequalities
            \item Finite outcome inequalities
        \end{itemize}
        \item Here we solve the marginal problem for $\mscenario = \PreInj[\graph]{\graph'}$
        \item First some notation and formalism
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Outcomes and Events}
    \begin{definition}
        Each variable $v$ has finite set of \term{outcomes} $O_v$. \\
        Each set of variables $V$ has finite set of \term{events} $\Events{V}$:
        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
    \end{definition}
    \begin{definition}
        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
    \end{definition}
    \begin{definition}
        The set of events over the marginal contexts are the \term{marginal events}
        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
    \end{definition}
\end{frame}

\begin{frame}
    \frametitle{Distribution Vectors}
    \begin{definition}
        The \term{joint distribution vector} $\probvec^{\jointvar}$
        \[ \probvec^{\jointvar}_j = \prob[\jointvar][j] \quad \forall j \in \Events{\jointvar}\]
    \end{definition}
    \begin{definition}
        The \term{marginal distribution vector} $\probvec^{\mscenario}$
        \[ \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \quad \forall m \in \Events{\mscenario}, \Dom{m} \in \mscenario\]
    \end{definition}
    Can now write complete marginal problem as matrix multiplication:
    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \iff \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \]
\end{frame}

\begin{frame}
    \frametitle{Incidence Matrix}
    \begin{itemize}
        \item \term{Incidence matrix} $M$ is a bit-wise matrix
        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
        \item Column-indexed by joint events $j \in \Events{\jointvar}$
        \[ M_{m,j} = \begin{cases}
            1 & m = j|_{\Dom{m}} \\
            0 & \text{otherwise}
        \end{cases} \]
        \begin{gather*}
        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
        \end{gather*}

\begin{frame}[shrink=10]
    \frametitle{Example}
    Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$. The incidence matrix becomes:
    \[ M = \kbordermatrix{
        (A,B,C) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
        (A=0, B=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
        (A=0, B=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
        (A=1, B=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
        (A=1, B=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
        (B=0, C=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
        (B=0, C=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
        (B=1, C=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
        (B=1, C=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
        (A=0, C=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
        (A=0, C=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
        (A=1, C=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
        (A=1, C=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
    } \]
\end{frame}

\begin{frame}
    \frametitle{Marginal Linear Program}
    \begin{itemize}
        \item Obtain inequalities from incidence matrix $M$ and known incompatible distribution $\probvec^{\mscenario}$
    \end{itemize}
    \begin{columns}[T]
        \column{0.4\linewidth}%
            \term{Marginal LP}:%
            \begin{alignat*}{2}
                & \text{minimize:} \quad&& \emptyset \tcdot x\\
                & \text{subject to:} && x \succeq 0 \\
                & && M \tcdot x = \probvec^{\mscenario} \\
            \end{alignat*}%
        \column{0.4\linewidth}%
            \term{Dual Marginal LP}:%
            \begin{alignat*}{2}
                & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
                & \text{subject to:} && y \tcdot M \succeq 0 \\
            \end{alignat*}%
    \end{columns}
    \begin{itemize}
        \item $y$ is an \term{infeasibility certificate}:
        \[ y \tcdot M \tcdot x = y \tcdot \probvec^{\mscenario} \geq 0  \]
        \item \term{Infeasibility inequality}: $y \tcdot \probvec^{\mscenario} \geq 0$
        \item Most linear programing toolkits return certificates (\href[pdfnewwindow]{http://docs.mosek.com/8.0/pythonapi/optimizer-task-gety.html}{\textit{Mosek}}, \href[pdfnewwindow]{https://www.gurobi.com/documentation/6.5/refman/farkasdual.html}{\textit{Gurobi}}, \href[pdfnewwindow]{http://www-01.ibm.com/support/docview.wss?uid=swg21400058}{\textit{CPLEX}}, \href[pdfnewwindow]{http://cvxr.com/cvx/doc/basics.html\#dual-variables}{\textit{cvxr}}/\href[pdfnewwindow]{http://cvxopt.org/userguide/coneprog.html\#linear-cone-programs}{\textit{cvxopt}}.)
    \end{itemize}
    \note[item]{It is possible to derive non-contextuality inequalities from $M$ and a known incompatible distribution $\probvec^{\mscenario}$}
    \note[item]{Note the null objective; the minimization objective is trivially always zero}
    \note[item]{The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.}
    \note[item]{If \textit{feasible}, then there exists a vector $x$ that is a valid joint distribution vector $\probvec^{\jointvar}$.}
    \note[item]{Feasibility implies that $\probvec^{\jointvar} = x$.}
    \note[item]{Infeasibility implies contextuality}
\end{frame}

\begin{frame}
    \frametitle{Known Incompatible Distribution in The Triangle Scenario}
    \cite{Fritz_2012} provides quantum-accessible distribution incompatible with TS
    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Notes of Fritz Distribution}
    \begin{itemize}
        \item Proof contingent on perfect correlation between $C$ and pseudo-settings
        \item Proof not robust to noise
    \end{itemize}
    \begin{problem}[2.17 in \cite{Fritz_2012}]
        Find an example of non-classical quantum correlations in TS together with a proof of its non-classicality which does not hinge on Bell’s Theorem.
    \end{problem}
    \begin{itemize}
        \item ``...would be helpful to have inequalities...''
        \item Possible to find inequalities violated by $\prob[F]$ using the Large inflation of the TS
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Triangle Scenario Inequality}

>>>>

\usetheme[height=8mm]{Rochester} % Main Theme
\usecolortheme{default} % Color Theme
\usepackage{lmodern} % Optional to remove font size warnings

% \usepackage{pgfpages} % For viewing slides on the right
\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
\AtBeginNote{\scriptsize} % Make notes small
% \setbeameroption{show notes} % Shows notes
% \setbeameroption{show only notes} % Shows only notes
% \setbeameroption{show notes on second screen}
\usefonttheme[onlymath]{serif} % For serif font in math mode
\usepackage[backend=biber, style=authoryear, doi=false,isbn=false,url=false, citestyle=authoryear-comp]{biblatex} %

@@

\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

@@

\begin{frame}
    \frametitle{Causal Compatibility}
    \vfill
    \begin{center}
        Triangle Scenario
    \end{center}
    \[ \prob[ABC] = \int_{XYZ}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    \vfill
    \begin{center}
        \noindent\rule{8cm}{0.4pt}
    \end{center}
    \vfill
    \begin{center}
        General Setting
    \end{center}
    \begin{align*}
    \mscenario &= \bc{V_1, \ldots, V_n} \\
    \prob^{\mscenario} &= \bc{\prob[V_1], \ldots, \prob[V_n]}
    \end{align*}
    \[ \forall V \in \mscenario: \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \]
    \[ \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
    \vfill
\end{frame}

\section{Part 1: Inflation Technique}
\begin{frame}
    \frametitle{Demonstrating Inflation Technique}
    \vfill
    \begin{center}
    \begin{columns}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_1}}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_1}}
    \end{columns}
    \end{center}
    \only<1>{\[\forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n}\]}%
    \only<2>{\[\AnSub[\graph]{A} \sim \AnSub[\graph']{A_1}\]}%
    \only<3>{\[\AnSub[\graph]{C} \sim \AnSub[\graph']{C_2}\]}%
\end{frame}

@@

\begin{frame}
    \frametitle{What are Injectable Sets?}
    \begin{center}
    \begin{columns}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_2}}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_2}}
    \end{columns}
    \end{center}
    \only<1>{\[\AnSub[\graph]{A,C} \sim \AnSub[\graph']{A_2,C_1}\]}%
    \only<2>{\[?? \not \sim \AnSub[\graph']{B_1,B_2}\]}%
    \only<3>{\[?? \not \sim \AnSub[\graph']{B_2,C_2}\]}%
\end{frame}

\begin{frame}
    \frametitle{Injectable Sets Defined}
    \vfill
    The \term{injectable sets in $\graph'$}:
    \begin{align*}
        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
    The \term{images of the injectable sets in $\graph$}:
    \begin{align*}
        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
    \vfill
    \begin{center}
        \textbf{What makes injectable sets useful?}
    \end{center}
    \vfill
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma}
    \begin{lemma}[Inflation Lemma]
    Given $\graph$ and inflation $\graph$':
    \begin{center}
        \begin{tikzpicture}
            \pgfmathsetmacro{\vs}{2.2};
            \pgfmathsetmacro{\hs}{5.2};
            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
            \draw[very thick, ->] (pn) -- (cp);
            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
            \draw[very thick, ->] (cp_) -- (pn_);
        \end{tikzpicture}
    \end{center}
    \end{lemma}
\end{frame}

\begin{frame}
    \frametitle{Perfect Correlation Is Incompatible}
    \begin{columns}
        \column{0.5\linewidth}
        \begin{center}
            \includegraphics[width=\linewidth]{../../figures/distributions/perfect_correlation_2_outcomes.pdf}
        \end{center}
        \column{0.5\linewidth}
        \begin{align*}
        \probplotvalue{0, 0, 0} &= \f12 \\
        \prob[ABC][abc] &= \f{\bs{000} + \bs{111}}{2} \\
        \prob[ABC][abc] &= \begin{cases}
            \f12 & a = b = c \\
            0 & \text{ otherwise }
        \end{cases}
        \end{align*}
    \end{columns}
    \begin{center}
        Compatibility Inequality
    \end{center}
    \[ \prob[A][0]\prob[B][1] \leq \prob[BC][10] + \prob[AC][01] \]
    \begin{center}
        Witnesses Perfect Correlation
    \end{center}
    \[ \br{\f{1}{2}}^{2} \not\leq 0 + 0 \]
\end{frame}
\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother
\begin{frame}
    \frametitle{Deriving Compatibility Inequalities}
    \begin{center}
        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
    \end{center}
    \[ \mscenario = \bc{\bc{A_1, B_1}, \bc{B_1, C_1}, \bc{A_1, C_1}} \]
    \[ \prob^{\mscenario} = \bc{\prob[A_1B_1], \prob[B_1C_1], \prob[A_1C_1]} \]
    \[ \text{Compatibility requires:} \qquad \exists \prob[\jointvar] = \prob[A_1B_1C_1] \]
    \[ \prob[A_1B_1] = {\sum}_{C_1} \prob[\jointvar] \qquad \prob[B_1C_1] = {\sum}_{A_1} \prob[\jointvar] \qquad \prob[A_1C_1] = {\sum}_{B_1} \prob[\jointvar]\]
\end{frame}

\begin{frame}[shrink=13]
    \frametitle{Deriving Compatibility Inequalities Cont'd}
    \[ \underbrace{\prob[A_1B_1] = {\sum}_{C_1} \prob[\jointvar] \qquad \prob[B_1C_1] = {\sum}_{A_1} \prob[\jointvar] \qquad \prob[A_1C_1] = {\sum}_{B_1} \prob[\jointvar]} \]
    \[ \underbrace{\forall V \in \mscenario: \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] }\]
    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}  \]
    \[ \probvec^{\mscenario} =
        \begin{pmatrix}
            \prob[A_1B_1][00] \\
            \prob[A_1B_1][01] \\
            \prob[A_1B_1][10] \\
            \prob[A_1B_1][11] \\
            \hline
            \prob[B_1C_1][00] \\
            \prob[B_1C_1][01] \\
            \prob[B_1C_1][10] \\
            \prob[B_1C_1][11] \\
            \hline
            \prob[A_1C_1][00] \\
            \prob[A_1C_1][01] \\
            \prob[A_1C_1][10] \\
            \prob[A_1C_1][11] \\
        \end{pmatrix}
        \qquad
        \probvec^{\jointvar} =
        \begin{pmatrix}
            \prob[A_1B_1C_1][000] \\
            \prob[A_1B_1C_1][001] \\
            \prob[A_1B_1C_1][010] \\
            \prob[A_1B_1C_1][011] \\
            \prob[A_1B_1C_1][100] \\
            \prob[A_1B_1C_1][101] \\
            \prob[A_1B_1C_1][110] \\
            \prob[A_1B_1C_1][111] \\
        \end{pmatrix}
    \]
\end{frame}

\begin{frame}[shrink=15]
    \frametitle{Incidence Example}
    \[ M = \kbordermatrix{
        (A_1,B_1,C_1) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
        (A_1=0, B_1=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
        (A_1=0, B_1=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
        (A_1=1, B_1=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
        (A_1=1, B_1=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
        (B_1=0, C_1=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
        (B_1=0, C_1=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
        (B_1=1, C_1=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
        (B_1=1, C_1=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
        (A_1=0, C_1=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
        (A_1=0, C_1=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
        (A_1=1, C_1=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
        (A_1=1, C_1=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
    } \]
    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}  \]
\end{frame}

\begin{frame}
    \frametitle{Marginal Linear Program}
    \begin{columns}[T]
        \column{0.4\linewidth}%
            \term{Marginal LP}:%
            \begin{alignat*}{2}
                & \text{minimize:} \quad&& \emptyset \tcdot x\\
                & \text{subject to:} && \probvec^{\jointvar} \succeq 0 \\
                & && M \tcdot \probvec^{\jointvar} = \probvec^{\mscenario} \\
            \end{alignat*}%
        \column{0.4\linewidth}%
            \term{Dual Marginal LP}:%
            \begin{alignat*}{2}
                & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
                & \text{subject to:} && y \tcdot M \succeq 0 \\
            \end{alignat*}%
    \end{columns}
    \begin{itemize}
        \item If $\probvec^{\jointvar}$ exists, then:
        \[ y \tcdot M \tcdot \probvec^{\jointvar} = y \tcdot \probvec^{\mscenario} \geq 0  \]
        \item If not, then $y$ is an \term{infeasibility certificate} which generates \term{infeasibility inequality}:
        \[ y \tcdot \probvec^{\mscenario} \geq 0 \]
        \item Most linear programing toolkits return certificates (\href[pdfnewwindow]{http://docs.mosek.com/8.0/pythonapi/optimizer-task-gety.html}{\textit{Mosek}}, \href[pdfnewwindow]{https://www.gurobi.com/documentation/6.5/refman/farkasdual.html}{\textit{Gurobi}}, \href[pdfnewwindow]{http://www-01.ibm.com/support/docview.wss?uid=swg21400058}{\textit{CPLEX}}, \href[pdfnewwindow]{http://cvxr.com/cvx/doc/basics.html\#dual-variables}{\textit{cvxr}}/\href[pdfnewwindow]{http://cvxopt.org/userguide/coneprog.html\#linear-cone-programs}{\textit{cvxopt}}.)
    \end{itemize}
    \note[item]{It is possible to derive non-contextuality inequalities from $M$ and a known incompatible distribution $\probvec^{\mscenario}$}
    \note[item]{Note the null objective; the minimization objective is trivially always zero}
    \note[item]{The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.}
    \note[item]{If \textit{feasible}, then there exists a vector $x$ that is a valid joint distribution vector $\probvec^{\jointvar}$.}
    \note[item]{Feasibility implies that $\probvec^{\jointvar} = x$.}
    \note[item]{Infeasibility implies contextuality}
\end{frame}

\begin{frame}
    \frametitle{Deflating Inequalities}
    \begin{columns}
        \column{0.5\linewidth}
            \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut_anim_1}}
        \column{0.5\linewidth}
            \vfill
            \begin{center}
            \[ \Inj[\graph]{\graph'} = \begin{Bmatrix}
                \bc{A_1,C_1}\\ \bc{B_1,C_1}\\ \bc{A_1}\\ \bc{B_1}\\ \bc{C_1}
            \end{Bmatrix} \]
            \[ \bc{A_1, B_1} \not \in \Inj[\graph]{\graph'} \]
            \end{center}
            \vfill
    \end{columns}
    \[ \prob[A_1B_1][01] \leq \prob[B_1C_1][10] + \prob[A_1C_1][01] \]
    \only<1>{\begin{center}\textbf{Can not deflate inequality!}\end{center}}
    \only<2>{\begin{center}\textbf{However!}\end{center}}
    \only<2>{\[ \AnSub[\graph']{A_1} \cap \AnSub[\graph']{B_1} = \emptyset \iff A_1 \ancestralindep B_1 \]}
    \onslide<3->{\[ \prob[A_1][0]\prob[B_1][1] \leq \prob[B_1C_1][10] + \prob[A_1C_1][01] \]}
    \onslide<4->{\[ \prob[A][0]\prob[B][1] \leq \prob[BC][10] + \prob[AC][01] \]}
\end{frame}

\begin{frame}
    \frametitle{Inflation Gives Polynomial Inequalities}
    \begin{itemize}
        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
        \item \textbf{Linear inequality} for $\graph'$
    \end{itemize}
    \begin{center}
        \begin{tikzpicture}[scale=0.8]
            \pgfmathsetmacro{\hs}{1.8};
            \pgfmathsetmacro{\vs}{1};
            \pgfmathsetmacro{\cross}{0.3};
            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
            \draw (0, 0) node[](b){??};
            \draw[thick, ] (a) -- (ab);
            \draw[thick, ] (c) -- (cd);
            \draw[thick, ] (a) -- (ac);
            \draw[thick, ->] (ac) -- (c);
            \draw[thick, ->] (ab) -- (b);
            \draw[thick, ->] (cd) -- (d);
            \draw[very thick, red]
            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
            ;
        \end{tikzpicture}
    \end{center}
    \begin{itemize}
        \item \textbf{Polynomial inequality} for $\graph$!
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pre-injectable Sets}
    A \term{pre-injectable set} $N'$ is:
    \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
    \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
    Only need to consider \term{maximal pre-injectable sets} denoted $\PreInj[\graph]{\graph'}$
\end{frame}

\section{Quantum Non-locality From Inflation}

\begin{frame}
    \frametitle{Quantum Correlation}
    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \quad \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2}
    \end{gather*}
    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
        M_{B} = \bc{\ket{0\psi_{6}}\bra{0\psi_{6}}, \ket{0\psi_{2}}\bra{0\psi_{2}}, \ket{1\psi_{0}}\bra{1\psi_{0}}, \ket{1\psi_{4}}\bra{1\psi_{4}}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Notes on Fritz Distribution}
    \begin{itemize}
        \item Incompatibility proof contingent on perfect correlation between $C$ and pseudo-settings
        \item Proof not robust to noise
    \end{itemize}
    \begin{problem}[2.17 in \cite{Fritz_2012}]
        Find an example of non-classical quantum correlations in TS together with a proof of its non-classicality which does not hinge on Bell’s Theorem.
    \end{problem}
    \begin{itemize}
        \item ``...would be helpful to have inequalities...''
        % \item Possible to find inequalities violated by $\prob[F]$ using the Large inflation of the TS
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Large Inflation}
    \begin{center}
        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{center}
\end{frame}

@@

% \begin{frame}
%     \frametitle{Deriving Inequalities}
%     \begin{itemize}
%         \item Inflation facilitates turning linear, inflated inequalities into polynomial deflated ones
%         \item \textbf{Question:} How to derive compatibility inequalities for $\graph'$?
%         \item \textbf{Answer:} Use your favorite technique for deriving compatibility inequalities:
%         \begin{itemize}
%             \item Entropic inequalities
%             \item Finite outcome inequalities
%         \end{itemize}
%         \item Here we solve the marginal problem for $\mscenario = \PreInj[\graph]{\graph'}$
%         \item First some notation and formalism
%     \end{itemize}
% \end{frame}

@@

\begin{frame}
    \frametitle{Certificate for Fritz Distribution}
    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
    \vfill
    \textbf{Note:} $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
\end{frame}
